An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-03 paper/5.experiments.tex
tiny

We introduced the composition $phead \circ phead$ earlier in Section~\ref{sec:intro}. The composition of many \textit{phead} 
% do things
works similarly. The head of a head element inside a 
%super 
deeply nested list, which 
% expresses 
is the source, 
% should be 
is updated by the changed view. Because of the type of the source, this program is 
% seen 
categorized as a \textit{ldata} case.

@@

$\putbx{ptail}{s}{v}$ accepts a source list $s$ and a view list $v$ to produce a new list by replacing the tail of $s$ with $v$. $\getbx{ptail}{s}$ returns the tail of the source list $s$. The composition of many $ptail$, in the \textit{put} direction, replaces a part of the tail of the source list by the view list and, in the \textit{get} direction, returns such a tail from the source.

$\putbx{bsnoc}{s}{v}$ accepts a source $s$ and a view $v$, 
%as two same length lists, 
which are two lists of the same length,
and produces a new list by moving the last element of $v$ to its first position. $\getbx{bsnoc}{s}$ returns another list by moving the first element of the list $s$ to its end position. The composition of many \textit{bsnoc}, in the \textit{put} direction, creates a permutation of the view list if the source list has a same length as the view and, in the \textit{get} direction, produces a permutation of the source list.

>>>>

We introduced the composition $phead \circ phead$ earlier in Section~\ref{sec:intro}. The composition of many \textit{phead}s 
% do things
works similarly. The head of a head element inside a 
%super 
deeply nested list, which 
% expresses 
is the source, 
% should be 
is updated by the changed view. Because of the type of the source, this program is 
% seen 
categorized as a \textit{ldata} case.

@@

$\putbx{ptail}{s}{v}$ accepts a source list $s$ and a view list $v$ to produce a new list by replacing the tail of $s$ with $v$. $\getbx{ptail}{s}$ returns the tail of the source list $s$. The composition of many $ptail$s, in the \textit{put} direction, replaces a part of the tail of the source list by the view list and, in the \textit{get} direction, returns such a tail from the source.

$\putbx{bsnoc}{s}{v}$ accepts a source $s$ and a view $v$, 
%as two same length lists, 
which are two lists of the same length,
and produces a new list by moving the last element of $v$ to its first position. $\getbx{bsnoc}{s}$ returns another list by moving the first element of the list $s$ to its end position. The composition of many \textit{bsnoc}s, in the \textit{put} direction, creates a permutation of the view list if the source list has a same length as the view and, in the \textit{get} direction, produces a permutation of the source list.
